# Labeling graph vertices

You can use the `points3d()` function to add labels to a plot, including graph
visualizations, in threejs. Labels are really just extra points in the plot
that happen to contain text.

Here is a simple example that adds names to the vertices of  the Les
Mis&eacute;rables character co-occurence graph.

The example below uses the new `vertices()` function to extract the plot vertex
coordinates from the widget. The `V(LeMis)$label` argument extracts the vertex
label names from the LeMis igraph graph object.

```{r, echo=TRUE, eval=FALSE}
library(threejs)
data(LeMis)
graphjs(LeMis) %>% points3d(vertices(.), color="red", pch=V(LeMis)$label, size=0.2)

# or equivalently without using the pipe:
g <- graphjs(LeMis)
points3d(g, vertices(g), color="red", pch=V(LeMis)$label, size=0.2)
```
```{r, echo=FALSE, eval=TRUE, fig.height=9, fig.width=12}
suppressMessages(
{
  library(threejs)
  data(LeMis)
  graphjs(LeMis) %>% points3d(vertices(.), color="red", pch=V(LeMis)$label, size=0.2)
})
```
