---
title: "globejs examples"
author: "B. W. Lewis"
date: "12/25/2014"
output:
  tufterhandout::html_tufte_handout:
    theme: spacelab
---

The *globejs* function plots surface maps
and data points on a sphere that you can
spin around and zoom. The function uses the
http://threejs.org 3-d visualization library and is part of the
*threejs* package for R, https://github.com/bwlewis/rthreejs.
You can install the *threejs* package using the *devtools* package:
```{r eval=FALSE,echo=TRUE}
devtools::install_github("bwlewis/rthreejs")
```

This document illustrates making globes from images or from maps
generated in R. The examples display in RStudio just like regular
R plots and can be used in shiny applications or stand-alone
web documents created with *rmarkdown* like this one. When viewing
from a web browser we find that recent versions of Google's chrome
and Internet Explorer work very well.

<aside>
```{r  echo=FALSE, marginfigure=TRUE, fig.width=4.5, fig.height=4.5}
library("threejs")
earth <- texture("/tmp/world.topo.bathy.200412.3x5400x2700.jpg")
globejs(img=earth, bg="#fcfcfa", emissive="#aaaacc")
```
</aside>

### Example 1: Using images as maps on the globe

Any image may be used as a surface map. For example, the globe on the right produced
by the following R code uses a beautiful high-resolution NASA "blue marble" MODIS
image downloaded from the web.
```{r  echo=TRUE, eval=FALSE}
library("threejs")
earth <- "http://eoimages.gsfc.nasa.gov/images/imagerecords/73000/73909/world.topo.bathy.200412.3x5400x2700.jpg"
globejs(img=earth, bg="white", emissive="#aaaacc")
```

You can plot points and bars over the globe by supplying data to the *lat* and *long* arguments,
using the *value* and *color* arguments to control the height and color of each bar.
Latitude and longitude values will only align properly with
plate carrée equirectangular projection maps, also known as lat/long maps.
Fortunately, lat/long map images are commonly available, and they're also
easy to create in R.

## Generating maps in R

An impressive variety of sophisticated cartographic packages are available
for R, and several of them can easily generate lat/long map images.
See the spatial task view  for a comprehensive list of available packages.

<aside>
http://cran.r-project.org/web/views/Spatial.html
</aside>


The *maptools* package by Roger Bivand and many contributors is a high-level plotting interface to
the *sp* package that greatly simplifies plotting regional and global maps.
Our examples illustrate making maps
for display on the globe using the *maptools* package, but with minor modification the examples
will work with other R packages like the excellent new *rworldmap* package.

<aside>
http://cran.r-project.org/web/packages/maptools/
</aside>

### Example 2: Bono awareness index

We start with fun map that approximates one published in the
Onion's atlas of the planet earth (thanks to Andy South for referencing this in his
*rworldmap* package).

<aside>
Scott Dikkers,
<i>Our dumb world: the Onion's atlas of the planet Earth</i>, 73 ed.,
Little Brown & Co., 2007.
</aside>

This example illustrates generating a basic map with political boundaries. The countries
are colored according to a loose approximation of the Onion's "Bono awareness index."
The example illustrates the required plot parameters to display a basic map like this on the globe.

A facsimile of the Bono awareness index color data may be found on my website at
http://illposed.net/bono.rdata; the data are stored in a single-column R data frame whose
row names are labeled with country names, a sample of which is shown here:
```{r eval=TRUE, echo=TRUE}
load(url("http://illposed.net/bono.rdata"))
bono[c(33,51,126,180,209),,drop=FALSE]
```
The index data are factors with five levels. We'll use the factor levels to color
the countries in our map. The trickiest part of preparing a map for display with
*globejs* is setting up the plot parameters. The map needs to take up the entire
plot region (no margins), and lat/long maps must have a 2:1 aspect ratio. Note that
some of the map plotting functions available in R (including the *maptools* functions)
override plot parameters. We illustrate that in the example below by showing the
full set of required plot parameters, repeating the overridden ones in the *maptools* plot
function. The complicated looking function that computes the *map_palette* colors
simply darkens the default *heat.color* palette a bit.

<aside>
```{r  echo=FALSE, marginfigure=TRUE, fig.width=4.5, fig.height=4.5}
suppressPackageStartupMessages(library("maptools"))
data(wrld_simpl)                             # Basic country shapes
load(url("http://illposed.net/bono.rdata"))

bgcolor="#000025"
earth=tempfile(fileext=".jpg")
jpeg(earth, width=2048, height=1024, quality=100, bg=bgcolor, antialias="default")
par(mar = c(0,0,0,0),    pin = c(4,2),    pty = "m",    xaxs = "i",
    xaxt = "n",          xpd = FALSE,    yaxs = "i",    yaxt = "n")

map_palette <- apply(col2rgb(heat.colors(5)[5:1])/768,2,function(x)rgb(x[1],x[2],x[3]))
# Restrict bono data to countries from the maptools package
bono <- bono[rownames(bono) %in% wrld_simpl$NAME, ,drop=FALSE]
# Set a default color for each country and the colors from the bono data
clrs <- rep(map_palette[1], length(wrld_simpl$NAME))
names(clrs) <- wrld_simpl$NAME
clrs[rownames(bono)] <- map_palette[bono$index]

plot(wrld_simpl,  col=clrs,   bg=bgcolor,        border="cyan",  ann=FALSE,
     axes=FALSE,  xpd=FALSE,  xlim=c(-180,180), ylim=c(-90,90),  setParUsrBB=TRUE)

graphics.off()

globejs(earth, bg="#fcfcfa")
```
<div style="width: 250px;">
<font color="#7f7f40">Has heard of nation once</font><br/><br/>
<font color="#7f7f00">Only thinks about nation when drawing up U2 tour schedule</font><br/><br/>
<font color="#7f5500">Frequently dedicates songs to nation</font><br/><br/>
<font color="#7f2a00">Moved enough by nation's crisis to momentarily remove sunglasses</font><br/><br/>
<font color="#7f0000">Cares about welfare of nation nearly as much as his own</font><br/><br/>
</div>
</aside>

```{r eval=FALSE}
library("maptools")
data(wrld_simpl)                             # Basic country shapes
load(url("http://illposed.net/bono.rdata"))  # Awareness index data

bgcolor <- "#000025"
earth <- tempfile(fileext=".jpg")
jpeg(earth, width=2048, height=1024, quality=100, bg=bgcolor, antialias="default")
par(mar = c(0,0,0,0),    pin = c(4,2),    pty = "m",    xaxs = "i",
    xaxt = "n",          xpd = FALSE,    yaxs = "i",    yaxt = "n")

map_palette <- apply(col2rgb(heat.colors(5)[5:1])/768,2,function(x)rgb(x[1],x[2],x[3]))
# Restrict bono data to countries from the maptools package
bono <- bono[rownames(bono) %in% wrld_simpl$NAME, ,drop=FALSE]
# Set a default color for each country and the colors from the bono data
clrs <- rep(map_palette[1], length(wrld_simpl$NAME))
names(clrs) <- wrld_simpl$NAME
clrs[rownames(bono)] <- map_palette[bono$index]

plot(wrld_simpl,  col=clrs,   bg=bgcolor,        border="cyan",  ann=FALSE,
     axes=FALSE,  xpd=FALSE,  xlim=c(-180,180), ylim=c(-90,90),  setParUsrBB=TRUE)

graphics.off()

legendcol=heat.colors(5)[5:1]
globejs(earth,  bg="white")
```

Use R jpeg or PNG antialiasing to produce smoother-looking border and boundary lines in your map image.
Note that the image background must be the same as the plot background or antialiasing can result in
image edge artifacts. Those artifacts become objectionably visible when the left and right edges are
glued together on the globe.

WebGL viewers may also notice some polar distortion that dissipates as the plot is zoomed in
(less noticeable in Canvas renderings). We're working on improving that...


### Example 3: Adding bars to make a spiky globe

Our motivation for this package was the well-known spiky globe visualization 
http://data-arts.appspot.com/globe/. We can use the *globejs* function to plot
bars over the globe on arbitrary points with just a few lines of code.

The example also illustrates using a custom map generated by R, highlighting a
country (Brazil), and adjusting the initial map rotation to bring the highlighted
country to the front.

<aside>
```{r  echo=FALSE, marginfigure=TRUE, fig.width=4.5, fig.height=4.5}
library("threejs")
library("maptools")
library("maps")
data(wrld_simpl, package="maptools")
data(world.cities, package="maps")
cities <- world.cities[order(world.cities$pop,decreasing=TRUE)[1:1000],]
value  <- 100 * cities$pop / max(cities$pop)


bgcolor <- "#000025"
earth <- tempfile(fileext=".jpg")
jpeg(earth, width=2048, height=1024, quality=100, bg=bgcolor, antialias="default")
par(mar = c(0,0,0,0), pin = c(4,2), pty = "m", xaxs = "i",
    xaxt = "n", xpd = FALSE, yaxs = "i", yaxt = "n")

col <- rep("black",length(wrld_simpl$NAME))    # Set a default country color
col[wrld_simpl$NAME=="Brazil"] <- "#003344"    # Highlight Brazil

plot(wrld_simpl, col=col,          bg=bgcolor, border="#111111", ann=FALSE,  axes=FALSE, 
     xpd=FALSE,  xlim=c(-180,180), ylim=c(-90,90),  setParUsrBB=TRUE)

graphics.off()

globejs(img=earth,         lat=cities$lat, long=cities$long, value=value, 
        rotationlat=-0.34, rotationlong=-0.38)
```
</aside>



```{r eval=FALSE}
library("threejs")
library("maptools")
library("maps")
data(wrld_simpl, package="maptools")
data(world.cities, package="maps")
cities <- world.cities[order(world.cities$pop,decreasing=TRUE)[1:1000],]
value  <- 100 * cities$pop / max(cities$pop)


bgcolor <- "#000025"
earth <- tempfile(fileext=".jpg")
jpeg(earth, width=2048, height=1024, quality=100, bg=bgcolor, antialias="default")
par(mar = c(0,0,0,0), pin = c(4,2), pty = "m", xaxs = "i",
    xaxt = "n", xpd = FALSE, yaxs = "i", yaxt = "n")

col <- rep("black",length(wrld_simpl$NAME))    # Set a default country color
col[wrld_simpl$NAME=="Brazil"] <- "#003344"    # Highlight Brazil

plot(wrld_simpl, col=col,          bg=bgcolor, border="#111111", ann=FALSE,  axes=FALSE, 
     xpd=FALSE,  xlim=c(-180,180), ylim=c(-90,90),  setParUsrBB=TRUE)

graphics.off()

globejs(img=earth, bg="black", lat=cities$lat,     long=cities$long, value=value, 
        rotationlat=-0.34,     rotationlong=-0.38, fov=30)
```
