---
title: "globejs examples"
author: "B. W. Lewis"
date: "12/25/2014"
output:
  tufterhandout::html_tufte_handout:
    theme: spacelab
---

The *globejs* function plots surface maps
and data points on a sphere that you can
spin around and zoom. The function uses the
http://threejs.org 3-d visualization library and is part of the
*threejs* package for R, https://github.com/bwlewis/rthreejs.
You can install the *threejs* package using the *devtools* package:
```{r eval=FALSE,echo=TRUE}
devtools::install_github("bwlewis/rthreejs")
```

This document illustrates making globes from images or from maps
generated in R. The examples display in RStudio just like regular
R plots and can be used in shiny applications or stand-alone
web documents created with *rmarkdown* like this one. When viewing
from a web browser we find that recent versions of Google's chrome
and Internet Explorer work very well.

<aside>
```{r  echo=FALSE, marginfigure=TRUE, fig.width=4.5, fig.height=4.5}
suppressMessages({
library("threejs")
earth <- texture("/tmp/world.topo.bathy.200412.3x5400x2700.jpg")
globejs(img=earth, bg="#fcfcfa", emissive="#111122")
})
```
</aside>

### Example 1: Using images as maps on the globe

Any image may be used as a surface map. For example, the globe on the right produced
by the following R code uses a beautiful high-resolution NASA "blue marble" MODIS
image downloaded from the web.
```{r  echo=TRUE, eval=FALSE}
library("threejs")
earth <- "http://eoimages.gsfc.nasa.gov/images/imagerecords/73000/73909/world.topo.bathy.200412.3x5400x2700.jpg"
globejs(img=earth, bg="white")
```

You can plot points and bars over the globe by supplying data to the *lat* and *long* arguments,
using the *value* and *color* arguments to control the height and color of each bar.
Latitude and longitude values will only align properly with
plate carrée equirectangular projection maps, also known as lat/long maps.
Fortunately, lat/long map images are commonly available, and they're also
easy to create in R.

## Generating maps in R

An impressive variety of sophisticated cartographic packages are available
for R, and several of them can easily generate lat/long map images.
See the spatial task view  for a comprehensive list of available packages.

<aside>
http://cran.r-project.org/web/views/Spatial.html
</aside>


The *maptools* package by Roger Bivand and many contributors is a high-level plotting interface to
the *sp* package that greatly simplifies plotting regional and global maps.
Our examples illustrate making maps
for display on the globe using the *maptools* package, but with minor modification the examples
will work with other R packages like the excellent new *rworldmap* package.

<aside>
http://cran.r-project.org/web/packages/maptools/
</aside>


### Example 2: Adding bars to make a spiky globe

Our motivation for this package was the well-known spiky globe visualization 
http://data-arts.appspot.com/globe/. We can use the *globejs* function to plot
bars over the globe on arbitrary points with just a few lines of code.

<aside>
```{r  echo=FALSE, marginfigure=TRUE, fig.width=4.5, fig.height=4.5}
suppressMessages({
library("threejs")
library("maptools")
library("maps")
data(world.cities, package="maps")
cities <- world.cities[order(world.cities$pop,decreasing=TRUE)[1:1000],]
value  <- 100 * cities$pop / max(cities$pop)

globejs(lat=cities$lat, long=cities$long, value=value, 
        rotationlat=-0.34, rotationlong=-0.38)
})
```
</aside>



```{r eval=FALSE}
library("threejs")
library("maptools")
library("maps")
data(world.cities, package="maps")
cities <- world.cities[order(world.cities$pop,decreasing=TRUE)[1:1000],]
value  <- 100 * cities$pop / max(cities$pop)

globejs(bg="black", lat=cities$lat,     long=cities$long, value=value, 
        rotationlat=-0.34,     rotationlong=-0.38, fov=30)
```
