---
title: "graphjs"
author: "bwlewis"
date: "1/14/2016"
output: html_document
---

The new `grapjhs` function (an [html widget](http://htmlwidgets.org) and part of the [threejs](http://bwlewis.github.io/rthreejs) package), makes it easy to plot
interactive 3-d force directed graphs.

This vignette explores the `graphjs` function using the `LeMis` data included in
the `threejs` package. The `LeMis` data contain character coappearance data for
Victor Hugo's novel Les Mis&eacute;rables, compiled in the Stanford Graph Database
by Donaled Knuth (see http://www-cs-faculty.stanford.edu/~uno/sgb.html) and taken from
the D3.js force directed graph example by Mike Bostock (http://bl.ocks.org/mbostock/4062045).

We explore the `graphjs` function by looking at the graph of character coappearance
in Les Mis&eacute;rables. We then illustrate a few measures of network centrality
and connectivity.

## Interactivity in graphjs

Plots produced by `graphjs` are primarily designed for mouse interaction. They
do also try to support touch interfaces with touch analogs of the indicated
mouse operations.

* Move the mouse over a node to show its label.
* Hold the left mouse button down and move the mouse to rotate the graph.
* Hold the right mouse button down and move the mouse to pan.
* Use the mouse scroll wheel to zoom in and out.
* Double-click on the plot to reset the view.

## A force directed graph

Let's plot a force directed graph of the characters in Les Mis&eacute;rables.
Each circle in the plot represents a character and an edge between circles
indicates that the corresponding characters interacted in the novel. The colors
are taken from http://bl.ocks.org/mbostock/4062045.

```{r, fig.width=9}
library(threejs)
data(LeMis)
graphjs(LeMis$edges, LeMis$nodes, bg="#fbfbfb")
```


## Degree centrality

Perhaps most intuitive measure of graph
centrality, degree centrality of a node simply counts the number of other nodes
it's connected to.

It turns out that many graph measurements are most easily computed using an
adjacency matrix representation of the graph. We can use the `graph2Matrix`
function to convert our node/edge list graph representation to a sparse matrix.
Degree centrality, for instance, is just a sum along columns of our adjacency
matrix. Note that the graph used here is undirected, resulting in a symmetric
adjacency matrix.

The following example computes degree centrality and adjusts the sizes of the
nodes accordingly. Bigger nodes are connected to more nodes than smaller ones.
```{r, fig.width=9}
M = graph2Matrix(LeMis$edges, LeMis$nodes)
v = Matrix::colSums(M)
v = v/max(v)    # normalize
LeMis$nodes$size = 4*v
graphjs(LeMis$edges, LeMis$nodes, bg="#fbfbfb")
```


## Eigen centrality

One possibile criticism of degree centrality is that it does not take into account
how "important" the nodes connected to a given node are. Eigen centrality helps
to account for that by, loosely, recursively measuring degree centrality&mdash;that
is, nodes connected to other nodes that themselves highly connected receive more weight.

Eigen centrality is defined by the entries of the eigenvector of the adjacency
matrix associated with the largest eigenvalue. We can say "largest" eigenvalue
because our adjacency matrix is symmetric, and therefore its eigenvalues are real
numbers. The fact that there is a single, non-degenerate largest eigenvalue is
a consequence of the Perron-Frobenius theorem, one of the most beautiful results
in linear algebra.

The next example adjusts the sizes of the nodes by eigen centrality.
```{r, fig.width=9}
v = abs(eigen(M)$vector[,1])
v = v/max(v)
LeMis$nodes$size = 4*v
graphjs(LeMis$edges, LeMis$nodes, bg="#fbfbfb")
```


## f-subgraph centrality

Eigen centrality gives more weight to nodes that are connected to other nodes with
lots of connections. Other measures like f-subgraph centrality 
(see, for example, E. Estrada and D. J. Higham, Network properties revealed through matrix functions, SIAM Rev., 52 (2010), pp. 696–714.) adjust this concept to
emphasize shorter paths more than longer ones.

The next example illustrates f-subgraph centrality for the exponential
function f(x)=exp(x) using the matrix exponential function `expm` from R's
Matrix package.
```{r, fig.width=9}
library(Matrix)
v = diag(expm(M))
v = v/max(v)
LeMis$nodes$size = 4*v
graphjs(LeMis$edges, LeMis$nodes, bg="#fbfbfb")
```


## f-subgraph communicability

The off-diagonal elements of the matrix exponential used in the last example
can be interpreted as a measure of the ease of travel between nodes. That is,
nodes with many available paths between them of relatively short lengths have
larger off-diagonal entries.

The next example adjusts the plotted edge thickness by this f-subgraph
communicability for f=exp; node sizes are determined by f-subgraph centrality
as in the last example. This example colors the edges by the color of the
originating node. It also sets a minimum node size beacuse some of the nodes
in the last example are effectively invisible.
```{r, fig.width=9}
library(Matrix)
E = expm(M)
v = diag(E)
v = v/max(v)
v = pmax(0.1, v) # minimum node size
E = E * M
E = E / max(E)
LeMis$nodes$size = 4*v
LeMis$edges$size = 20*E@x
LeMis$edges$color = LeMis$nodes$color[LeMis$edges$from + 1]
graphjs(LeMis$edges, LeMis$nodes, bg="#fbfbfb")
```
