---
title: "Basic graphjs animation"
author: "bwlewis"
date: "1/31/2017"
output:
  html_document:
    css: style.css
---

This vignette explores basic graph animation with `graphjs`. The basic
animation idea defines the animation by a list of graphs and/or graph layouts.

Consider the `LeMis` character co-occurrence graph included with the
package. A static visualization using a force-directed vertex layout
looks like:

```{r, echo=FALSE, eval=TRUE}
suppressPackageStartupMessages(library(threejs, quietly=TRUE))
```
```{r, fig.width=9}
library(threejs)
data(LeMis)
graphjs(LeMis, layout=layout_with_fr(LeMis, dim=3))
```

<br/>
<a href="vertex.html">Click here to proceed to a vertex animation example.</a>


## Contents

- <a href="animation.html">Start</a>
- <a href="vertex.html">Basic vertex animation</a>
- <a href="color.html">Basic vertex animation with color</a>
- <a href="edge.html">Basic edge animation</a>
- <a href="../index.html">Back to threejs gallery</a>

<br/>
<br/>
<br/>
<br/>
<br/>
<br/>
