---
output:
  html_document:
    css: style.css
---

# Vertex animation with color

This example is nearly identical to the last one. It displays a number
of vertex layouts for the `LeMis` graph in sequence, but changes the
vertex colors while doing so. Similarly to layouts, specify animated
colors as a list.
```{r, echo=FALSE, eval=TRUE}
suppressPackageStartupMessages(library(threejs, quietly=TRUE))
```
```{r, fig.width=9}
library(threejs)
data(LeMis)
N <- length(V(LeMis))  # number of vertices
graphjs(LeMis,
        layout=list(layout_randomly(LeMis, dim=3),
                    layout_on_sphere(LeMis),
                    layout_with_drl(LeMis, dim=3),
                    layout_with_fr(LeMis, dim=3)),
        vertex.color=list(rainbow(N),
                          "blue",
                          "orange",
                          rainbow(N)),
        main=list("random layout", "sphere layout",
                  "drl layout", "fr layout"),
        fpl=300)
```

## Notes

You may have noticed that the default edge color scheme interpolates
between the vertices at each end. You can also explicitly specify
edge colors with the `edge.color` option, and animate among those
as above by supplying a list.

## Limitations

Vertex colors may include alpha (transparency) and will be adjusted
as specified. Edge colors, however, ignore transparency. Instead you
can only set an overall edge transparency value with the `edge.alpha`
parameter.

<br/>
<a href="edge.html">Click here to proceed to an edge animation example.</a>

## Contents

- <a href="animation.html">Start</a>
- <a href="vertex.html">Basic vertex animation</a>
- <a href="color.html">Basic vertex animation with color</a>
- <a href="edge.html">Basic edge animation</a>
- <a href="../index.html">Back to threejs gallery</a>

<br/>
<br/>
<br/>
<br/>
<br/>
<br/>
