---
output:
  html_document:
    css: style.css
---

# Edge animation

We illustrate edge animation with a simpler example to make it easy to see the
effect. Our example begins as a trivially simple graph of only five vertices
and no edges between them.

The animation proceeds by adding edges one by one. Similarly to vertex
animation examples where lists of layouts define the animation sequence,
edge animation requires a list of igraph objects with different edges.

```{r, echo=FALSE, eval=TRUE}
suppressPackageStartupMessages(library(threejs, quietly=TRUE))
```
```{r, fig.width=9}
g <- make_ring(5) - edges(1:5) # five vertices, no edges

graph_list <- list(
  g + edge(1, 2),
  g + edge(1, 2) + edge(2, 3),
  g + edge(1, 2) + edge(2, 3) + edge(3, 4),
  g + edge(1, 2) + edge(2, 3) + edge(3, 4) + edge(4, 5),
  g + edge(1, 2) + edge(2, 3) + edge(3, 4) + edge(4, 5) + edge(5, 1))

graphjs(graph_list, main=paste(1:5),
        vertex.color=rainbow(5), vertex.shape="sphere", edge.width=3)
```

## Notes

You can of course supply a list of layouts too, to control animation of both
edges and vertex positions. Since no layouts were specified, a default vertex
layout was generated for each scene in the above example.

## Contents

- <a href="animation.html">Start</a>
- <a href="vertex.html">Basic vertex animation</a>
- <a href="color.html">Basic vertex animation with color</a>
- <a href="edge.html">Basic edge animation</a>
- <a href="../index.html">Back to threejs gallery</a>

<br/>
<br/>
<br/>
<br/>
<br/>
<br/>
