---
output:
  html_document:
    css: style.css
---

# Vertex animation

Let's say that we want to display a number of different vertex layouts
as an animated sequence. Simply specify a list of layouts in the
`layout` parameter instead of a single layout. For instance
(you can interact with the plot during the animation):
```{r, echo=FALSE, eval=TRUE}
suppressPackageStartupMessages(library(threejs, quietly=TRUE))
```
```{r, fig.width=9}
library(threejs)
data(LeMis)
graphjs(LeMis,
        layout=list(layout_randomly(LeMis, dim=3),
                    layout_on_sphere(LeMis),
                    layout_with_drl(LeMis, dim=3),
                    layout_with_fr(LeMis, dim=3)),
        main=list("random layout", "sphere layout",
                  "drl layout", "fr layout"),
        fpl=300)
```
Note that we also supplied a list of main title text, one title corresponding
to each layout. The `fpl=300` parameter the (linear) interpolating steps
between each layout to 300 in this example.

## Notes

The following graphjs() function parameters
may be supplied as lists for animation:

- graph object
- layout
- vertex.color
- edge.color
- main  (title text)

Similarly to igraph, options like vertex color and edge color
can alternatively be defined within the graph objects. If both
styles of specification are used, the explicit function parameter
version takes precedence.

## Limitations

Each layout must include the same number of vertices. This limitation is
imposed for performance reasons. Althoug the number of vertices must remain
constant during the animation, their color and transparency values may be
changed dynamically as shown in the next example below.

<br/>
<a href="color.html">Click here to proceed to an animation example with different colors.</a>


## Contents

- <a href="animation.html">Start</a>
- <a href="vertex.html">Basic vertex animation</a>
- <a href="color.html">Basic vertex animation with color</a>
- <a href="edge.html">Basic edge animation</a>
- <a href="../index.html">Back to threejs gallery</a>

<br/>
<br/>
<br/>
<br/>
<br/>
<br/>
